Benchmarking FDR Methods - Alternative Settings

### 2017-10-20 datasets/simulations/analysis-01-plot.Rmd
Update analysis to point to new dir structure

<!-- ######################################################################## -->
<!-- preliminaries                                                            --> 
<!-- ######################################################################## -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, install-benchmarked-methods, eval=FALSE}
## from CRAN
install.packages("ashr")

## from Bioconductor
BiocInstaller::biocLite("IHW")
BiocInstaller::biocLite("qvalue")
BiocInstaller::biocLite("swfdr")

## from GitHub
devtools::install_github('jgscott/FDRreg', subdir="R_pkg/")
devtools::install_github("nignatiadis/IHWpaper")
```

@@

```{r, load-helper-functions}
source("analysis-01-plotters.R")
source("../datasets/R/evaluation-helpers.R")
```

```{r}
## list of results from 100 replication experiments
fl <- list.files("data", pattern="results-.*-M100.RDS", full.names=TRUE)

## generate same plots for all parameter settings
for (f in fl) {
    ## read process data
    res <- readRDS(f)
    tsb <- standardize_results(res, alpha = seq(0.01, 0.10, 0.01))
    tsbs <- tsb %>%
        filter(!(blabel %in% c("bl-df02", "bl-df04", "bl-df05", "bonf")))

    ## look at FPR for Boca-Leek variations
    gp <- tsb %>%
        filter(grepl("^bl-", blabel)) %>%
        average_plots("FPR")
    ggsave(paste0("plots/FPR-bocaleek-",
                  gsub("(.*)\\.RDS", "\\1", basename(f)), ".png"), gp,
           width=7, height=6, units="in", dpi=200)

    ## look at FPR for IHW variations
    gp <- tsb %>%
        filter(grepl("^ihw-", blabel)) %>%
        average_plots("FPR", merge_ihw = FALSE)
    ggsave(paste0("plots/FPR-ihw-",
                  gsub("(.*)\\.RDS", "\\1", basename(f)), ".png"), gp,
           width=7, height=6, units="in", dpi=200)

    ## make plots for all metrics
    for (im in unique(tsbs$performanceMetric)) {
        gp <- average_plots(tsbs, im, clean_names = TRUE)
        ggsave(paste0("plots/", im, "-", gsub("(.*)\\.RDS", "\\1", basename(f)), ".png"), gp,
               width=7, height=6, units="in", dpi=200)
    }
}
```

@@

```{r}
## list of results from 1 replication experiments
fl <- list.files("data", pattern = "results-.*-M1.rdata", full.names = TRUE)

@@

    ## adjusted p-values vs. effect size
    gp <- single_plots(sbas, sim_df, "effect_size", TRUE)
    ggsave(paste0("plots/effectsize-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
           gp, width=10, height=9, units="in", dpi=200)

    ## adjusted p-values vs. independent covariate (uniformative)
    gp <- single_plots(sbas, sim_df, "ind_covarate", TRUE)
    ggsave(paste0("plots/indcov-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
           gp, width=10, height=9, units="in", dpi=200)

    ## adjusted p-values vs. standard error
    gp <- single_plots(sbas, sim_df, "SE", TRUE)
    ggsave(paste0("plots/SE-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
           gp, width=10, height=9, units="in", dpi=200)
}
```

>>>>

@@

```{r, load-helper-functions}
source("../R/plotsim_standardize.R")
source("../R/plotsim_average.R")
source("../R/plotsim_single.R")
```

@@

```{r}
## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M1", recursive=FALSE, full.names=TRUE)

for (dd in dl) {
    fl <- list.files(dd, pattern=".rdata", full.names=TRUE)

    outp <- gsub("data", "plots", dd)
    dir.create(outp, showWarnings=FALSE, recursive=TRUE)

@@

        ## adjusted p-values vs. effect size
        gp <- plotsim_single(sbas, sim_df, "effect_size", TRUE)
        ggsave(paste0(outp, "/effectsize-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=9, units="in", dpi=200)

        ## adjusted p-values vs. independent covariate (uniformative)
        gp <- plotsim_single(sbas, sim_df, "ind_covariate", TRUE)
        ggsave(paste0(outp, "/indcov-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=9, units="in", dpi=200)

        ## adjusted p-values vs. standard error
        gp <- plotsim_single(sbas, sim_df, "SE", TRUE)
        ggsave(paste0(outp, "/SE-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=9, units="in", dpi=200)
    }
}
```

```{r}
## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M100", recursive=FALSE, full.names=TRUE)

for (dd in dl) {
    fl <- list.files(dd, pattern=".rds", full.names=TRUE)

    outp <- gsub("data", "plots", dd)
    dir.create(outp, showWarnings=FALSE, recursive=TRUE)

    ## generate same plots for all parameter settings
    for (f in fl) {
        ## read process data
        res <- readRDS(f)
        tsb <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))
        tsbs <- tsb %>%
            filter(!(blabel %in% c("bl-df02", "bl-df04", "bl-df05", "bonf")))

        ## look at FPR for Boca-Leek variations
        gp <- tsb %>%
            filter(grepl("^bl-", blabel)) %>%
            plotsim_average("FPR")
        ggsave(paste0(outp, "/FPR-bocaleek-",
                      gsub("(.*)\\.rds", "\\1", basename(f)), ".png"), gp,
               width=7, height=6, units="in", dpi=200)

        ## look at FPR for IHW variations
        gp <- tsb %>%
            filter(grepl("^ihw-", blabel)) %>%
            plotsim_average("FPR", merge_ihw = FALSE)
        ggsave(paste0(outp, "/FPR-ihw-",
                      gsub("(.*)\\.rds", "\\1", basename(f)), ".png"), gp,
               width=7, height=6, units="in", dpi=200)

        ## make plots for all metrics
        for (im in unique(tsbs$performanceMetric)) {
            gp <- plotsim_average(tsbs, im, clean_names = TRUE)
            ggsave(paste0(outp, "/", im, "-", gsub("(.*)\\.rds", "\\1", basename(f)), ".png"), gp,
                   width=7, height=6, units="in", dpi=200)
        }
    }
}
```
